Nail: A practical interface generator for binary formats

### 2014-04-01 paper/relwk.tex
move more relwk from intro to relwk

@@

>>>>

Parser generators for binary protocols were first introduced by the
Hammer\footnote{\url{http://github.com/upstandinghackers/hammer/}} parser.
While previous parser generators could also be used to write grammars
for binary protocols\footnote{Theoretically speaking, the alphabet
over which a grammar is an  abstract set, so most algorithms work
just as well on an alphabet of $\{0,1\}$}, doing so is impractically
inconvenient. Hammer allows the programmer to specify a grammar in
terms of bits and bytes instead of characters. Common concerns, such as
endianness and bit-packing are transparently hidden by the library. Hammer
implements grammars as language-integrated parser combinators, an approach
popularised by Parsec for Haskell~\cite{LeijenMeijer:parsec}. The
parser combinator style (to our knowledge, first  described
in~\cite{burge1975recursive}) is a natural way of concisely expressing
top-down grammars~\cite{Danielsson:2010:TPC:1863543.1863585}\footnote{For
more background on the history of expressing grammars, see Bryan Ford's
masters thesis~\cite{ford2002packrat}, which also describes the default
parsing algorithm used by Hammer} by composing them from one or multiple
sub-parsers.  Hammer then constructs a tree of function pointers which
can be invoked to parse a given input into an abstract syntax tree (AST).

@@

\paragraph{Application use of parsers.}

Unfortunately, grammars are seldom used directly to recognise
machine-created input. For example, the security-critical and very
well-engineered MIT Kerberos distribution uses parser generators, but
only for handling configuration files. A notable exception is the Mongrel
web server\footnote{\url{http://mongrel2.org/}} which uses a grammar
for HTTP written in the Ragel~\cite{ragel-paper} regular expression
language. Mongrel was re-written from scratch multiple times to achieve
better scaleability and design, yet the grammar could be  re-used across
all iterations~\cite{patterson-citation}.
